---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Kalam:wght@300;400;700&display=swap');

body {color: #DBB828;
      background-color: #3C3C3C;
      font-family: 'Kalam';
      padding: 20px
      }

H2 {font-weight: 500;
    color: #B4DBF7}

```

## The data is tracking the arrival status of a bus.

The data I tracked is the arrival status of a bus, seperated into 3 categories:
Early, On time, and Delayed. I decided to use the means, minimum and maximum of
Early and Late.

```{r}
# Makes it more convenient
library(tidyverse)

# Just adding data in
CSV <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSr345Q0vrXnLqhlRFBDyGyp6NIkG_HeEXcrBqEpToIjAtNqSbZ7ArFDt5XSRGpgIJTjgxVISvh9QeV/pub?output=csv"

logged_data <- read_csv(CSV) %>%
  rename(Early_min = 5,
         On_time_min = 8,
         Late_min = 6,
         Status = 4)

latest_data <- logged_data %>%
  select(Early_min, On_time_min, Late_min, Status)

# For pasting
Emean <- latest_data$Early_min %>% mean(na.rm = TRUE)
Emin <- latest_data$Early_min %>% min(na.rm = TRUE)
Emax <- latest_data$Early_min %>% max(na.rm = TRUE)

Lmean <- latest_data$Late_min %>% mean(na.rm = TRUE) %>% round(0)
Lmin <- latest_data$Late_min %>% min(na.rm = TRUE)
Lmax <- latest_data$Late_min %>% max(na.rm = TRUE)

```

## Early

The mean minutes of the bus early is `r Emean` mins.

The minimum minuteof the bus early is `r Emin` mins.

The maximum minute of the bus early is `r Emax` mins.

## Late

The mean of the minutes of the bus delayed is `r Lmean` mins.

The minimum minute of the bus delayed is `r Lmin` mins.

The maximum minute of the bus delayed is `r Lmax` mins.

## Bar Charts

## Late Frequency Bar Chart

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = Late_min, fill = Status)) +
  labs(title = "How late can a bus get?",
       subtitle = "Seeing the numbers of how late a bus is",
       caption = "Source: me",
       x = "Minutes",
       y = "Number of times")

```

On this first bar chart, it analyses the frequency of delays, and which minute
is more frequent. 2 and 4 minutes seem to be the most frequent when the bus is delayed.

## Status Bar Chart

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = Status, fill = Status)) +
  labs(title = "Which status is the more common?",
       subtitle = "Comparison of Early, On time, and Delayed",
       caption = "Source: me",
       x = "Status",
       y = "Number of times")

```

On this second bar chart, it analyses which arrival status of a bus is more
common. In my observations, Delay and On time seems to be equal. The bus doesnt
seem to come early that often. But then again, this is just a small sample.
